candidate genes

### 2019-12-15 analysis/10_specificgenes.Rmd
new colors

```{r candidategenes, fig.width =5.5, fig.height= 4}
candidategenes <- c("PRL","PRLR", "GNRHR")

@@

g <- plotcanddateexpression(candidates.hyp, "hypothalamus", candidates.hyp$GNRHR, "GNRHR")
h <- plotcanddateexpression(candidates.pit, "pituitary", candidates.pit$GNRHR, "GNRHR")
i <- plotcanddateexpression(candidates.gon, "gonad", candidates.gon$GNRHR, "GNRHR")

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)
dim(counts)
dim(cols)

x <- correlate(counts)
fashion(x)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

x %>% network_plot.cor_df(min_cor = .5) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

cal_z_score <- function(x){
  (x - mean(x)) / sd(x)
}

tcounts <- t(counts)
cols <- cols %>% select(-bird)

data_subset_norm <- t(apply(tcounts, 1, cal_z_score))
row.names(cols) <- colnames(data_subset_norm)

pheatmap(data_subset_norm,  annotation_col = cols)

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)
dim(counts)
dim(cols)

x <- correlate(counts)
fashion(x)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "bldg to lay")

x %>% network_plot.cor_df(min_cor = .5) + labs(subtitle = "bldg to lay")

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)
dim(counts)
dim(cols)

x <- correlate(counts)
fashion(x)
rplot(x) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "lay to inc.d3")

x %>% network_plot.cor_df(min_cor = .5)  + 
  labs(subtitle = "lay to inc.d3")

@@

counts <- full_join(candidates.pit, candidates.hyp) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.hyp) %>% drop_na() %>% select(bird, sex, treatment)
dim(counts)
dim(cols)

@@

x %>% network_plot.cor_df(min_cor = .5)  + 
  labs(subtitle = "hatch to n5")

>>>>

```{r candidategenes, fig.width =5.5, fig.height= 4}
candidategenes <- c("PRL","PRLR", "CRY1")

@@

g <- plotcanddateexpression(candidates.hyp, "hypothalamus", candidates.hyp$CRY1, "CRY1")
h <- plotcanddateexpression(candidates.pit, "pituitary", candidates.pit$CRY1, "CRY1")
i <- plotcanddateexpression(candidates.gon, "gonad", candidates.gon$CRY1, "CRY1")

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)

x <- correlate(counts)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62")) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)

x <- correlate(counts)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "bldg to lay")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62")) + 
  labs(subtitle = "bldg to lay")

@@

counts <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.gon) %>% drop_na() %>% select(bird, sex, treatment)

x <- correlate(counts)
rplot(x) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "lay to inc.d3")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62"))  + 
  labs(subtitle = "lay to inc.d3")

@@

counts <- full_join(candidates.pit, candidates.hyp) %>% drop_na() %>% select(-bird, -sex, -treatment)
cols <- full_join(candidates.pit, candidates.hyp) %>% drop_na() %>% select(bird, sex, treatment)

@@

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62"))  + 
  labs(subtitle = "hatch to n5")
